Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Add note about terrain elevation, Galin

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy. \textbf{(Fan et al, 2014)}
When we have the fundamental procedure for accuratly importing building footprints without compromising the data integritey, we can proceed with building modeling. \textbf{(Müller et al, 2006)} Other challenges include infering or guessing building height. () have presented a method for inferring building height from the building footprint alone, with surprising accuracy.

Building elevation. Occasinally buildings in OSM may be tagged, but the norm is that no elevation data is available.
\textbf{(Biljecki, Ledoux and Stoter, 2017)} presented a method for inferring building height exclusively from the building footprint and surrounding footprints.
Surprisingly, their model was shown to be accurace within a meter on average.

@@

>>>>

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy. \textbf{(Fan et al, 2014)}
When we have the fundamental procedure for accuratly importing building footprints without compromising the data integritey, we can proceed with building modeling. \textbf{(Müller et al, 2006)}

Terrain elevation. Elevation data is available from other sources, but not by OSM.
\textbf{(Galin et al, 2010)} present a geometrical model for placing a 3d road asset onto a non-flat terrain surface.

Other challenges include infering or guessing building height.
Occasinally buildings in OSM may be tagged, but the norm is that no elevation data is available.
\textbf{(Biljecki, Ledoux and Stoter, 2017)} presented a method for inferring building height exclusively from the building footprint and surrounding footprints.
Surprisingly, their model was shown to be accurace within a meter on average.

@@

\bibitem{galin-10}
Galin, E., Peytavie, A., Maréchal, N., and Guérin, E. (2010). Procedural Generation of Roads. Computer Graphics Forum. 29. 429 - 438. 10.1111/j.1467-8659.2009.01612.x.
